% Risks (MDPI) manuscript draft for the stock index volatility project.
\documentclass[risks,article,submit,moreauthors]{Definitions/mdpi}

\usepackage{bm}   % bold math symbols (\bm) -- required for spillover feature notation

\setlength{\headheight}{24pt}

\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2026}
\copyrightyear{2026}
\datereceived{}
\daterevised{}
\dateaccepted{}
\datepublished{}
\Title{Public-Data Causal Multiscale Wavelet Spillover Learning for Stock Index Volatility Forecasting and Risk Early Warning}

\definecolor{BestTone}{HTML}{E7D7A6}
\definecolor{SecondTone}{HTML}{EBCBB7}
\definecolor{ThirdTone}{HTML}{D9E1E8}
\newcommand{\best}[1]{\cellcolor{BestTone}\textbf{#1}}
\newcommand{\second}[1]{\cellcolor{SecondTone}\underline{#1}}
\newcommand{\third}[1]{\cellcolor{ThirdTone}{#1}}

\newcommand{\orcidauthorA}{0009-0007-0602-7924}
\newcommand{\orcidauthorB}{0009-0009-2858-6318}
\newcommand{\orcidauthorC}{0000-0002-4822-9627}

\Author{Hengyan Liu $^{1}$\orcidA{}, Yisu Shen $^{1}$\orcidB{} and Aiping Jiang $^{2,}$*\orcidC{}}
\AuthorNames{Hengyan Liu, Yisu Shen and Aiping Jiang}

\address{%
$^{1}$ \quad Sino-European School of Technology, Shanghai University, Shanghai 200444, China; hengyan@shu.edu.cn (H.L.); yisu@shu.edu.cn (Y.S.) \\
$^{2}$ \quad SHU-UTS SILC Business School, Shanghai University, Jiading District, Shanghai 201800, People's Republic of China; ajiang@shu.edu.cn (A.J.)}

\corres{Correspondence: ajiang@shu.edu.cn}

\abstract{Accurate volatility forecasting and timely risk early warning are foundational requirements of financial risk management: Value-at-Risk estimates, portfolio risk limits, derivative hedging ratios, and stress-test scenario calibrations all depend on forward-looking volatility signals that remain reliable when market conditions depart from average. This paper develops a public-data Causal Multiscale Wavelet Spillover Learning (CMWSL) framework that jointly addresses stock-index volatility forecasting and high-volatility early warning under strict walk-forward evaluation. CMWSL integrates three components: a heterogeneous autoregressive (HAR) persistence block as the dominant linear baseline, causal stationary wavelet transform (SWT) summaries that encode within-index multiscale market dynamics, and a cross-index spillover layer that tests whether medium- and long-scale wavelet energy from peer indices carries incremental risk-relevant information. The empirical analysis covers the S\&P~500, Nasdaq-100, and Dow Jones Industrial Average over a 2513-step out-of-sample evaluation period from 2016 to 2025, with forecast horizons $h \in \{1,5,10\}$ and OHLC-based volatility targets. HAR remains the strongest average model in the main Rogers--Satchell specification, confirming that daily index volatility risk is highly persistence-driven. The multiscale extension delivers statistically significant improvements at longer horizons, in richer public macro-financial information environments, and under the Parkinson target. Clark--West tests detect significant spillover gains in five of nine index--horizon cells (CW\,$=4.83$, $p<0.001$ for S\&P~500 at $h=10$). Critically, tail-conditioned and rolling-window diagnostics show that multiscale and cross-index gains concentrate in upper-volatility regimes and synchronized stress episodes---precisely the conditions in which risk management decisions are most consequential. For market-risk early warning, a logistic classifier built on the same causal feature pipeline delivers the most stable precision--recall performance across all settings, providing an interpretable and operationally auditable alert mechanism suitable for practical risk monitoring.}

\keyword{financial risk management; stock index volatility forecasting; risk early warning; stationary wavelet transform; multiscale learning; wavelet spillover; HAR model; walk-forward evaluation; tail risk; market risk monitoring}

\begin{document}

\section{Introduction}\label{sec:introduction}
\input{sections/01_introduction}

\section{Data}\label{sec:data}
\input{sections/02_data}

\section{Methodology}\label{sec:methodology}
\input{sections/03_methodology}

\section{Experimental Design}\label{sec:design}
\input{sections/04_experimental_design}

\section{Results}\label{sec:results}
\input{sections/05_results}

\section{Discussion}\label{sec:discussion}
\input{sections/06_discussion}

\section{Conclusions}\label{sec:conclusions}
\input{sections/07_conclusions}

\authorcontributions{Conceptualization, H.L., Y.S. and A.J.; methodology, H.L.; software, H.L.; validation, H.L. and Y.S.; formal analysis, H.L.; investigation, H.L.; data curation, H.L.; writing---original draft preparation, H.L.; writing---review and editing, H.L., Y.S. and A.J.; visualization, H.L.; supervision, A.J. All authors have read and agreed to the published version of the manuscript.}

\funding{This research received no external funding.}

\institutionalreview{Not applicable.}

\informedconsent{Not applicable.}

\dataavailability{The raw market data used in this study are publicly accessible from Stooq (\url{https://stooq.com}) and the Federal Reserve Economic Data (FRED) platform (\url{https://fred.stlouisfed.org}). The repository snapshot used to generate this manuscript contains a structured reviewer reproducibility package with dependency specifications, experiment configuration files, data-construction scripts, evaluation launchers, merged prediction outputs, and figure-generation scripts sufficient to regenerate the reported tables and figures. These materials are organized in the project repository at \url{https://github.com/lawhayee-bit/volatility-wavelet-spillover} and can be shared directly with editors and reviewers during evaluation.}

\acknowledgments{The authors thank colleagues and reviewers for their constructive suggestions during the development of this study.}

\conflictsofinterest{The authors declare no conflicts of interest.}

\abbreviations{Abbreviations}{
\noindent
\begin{tabular}{@{}ll}
ATR & Average true range \\
CMWSL & Causal multiscale wavelet spillover learning \\
DM & Diebold--Mariano \\
EGARCH & Exponential generalized autoregressive conditional heteroskedasticity \\
ETF & Exchange-traded fund \\
FRED & Federal Reserve Economic Data \\
GARCH & Generalized autoregressive conditional heteroskedasticity \\
HAR & Heterogeneous autoregressive \\
OHLC & Open--high--low--close \\
PR-AUC & Area under the precision--recall curve \\
QLIKE & Quasi-likelihood loss \\
RS & Rogers--Satchell \\
SWT & Stationary wavelet transform
\end{tabular}
}

\appendixtitles{yes}
\appendixstart
\appendix
\section{Supplementary Experimental Notes}
\input{supplement/appendix}

\begin{adjustwidth}{-\extralength}{0cm}
\reftitle{References}
\bibliography{bib/references}
\end{adjustwidth}

\end{document}
