\documentclass[11pt, a4paper]{letter}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{microtype}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\address{%
  Aiping Jiang\\
  SHU-UTS SILC Business School\\
  Shanghai University\\
  Jiading District, Shanghai 201800, China\\
  \href{mailto:ajiang@shu.edu.cn}{ajiang@shu.edu.cn}
}

\date{26 May 2026}

\signature{Aiping Jiang\\(Corresponding Author, on behalf of all authors)}

\begin{document}

\begin{letter}{%
  Editorial Office\\
  \textit{Risks}\\
  MDPI AG, St.\ Alban-Anlage 66\\
  4052 Basel, Switzerland
}

\opening{Dear Editors,}

Please find enclosed the revised version of our manuscript entitled

\begin{center}
  \textbf{``Public-Data Causal Multiscale Wavelet Spillover Learning for\\
  Stock Index Volatility Forecasting and Risk Early Warning''}
\end{center}

\noindent resubmitted for consideration as an \textit{Article} in
\textit{Risks}.

We thank the reviewers for their careful and constructive evaluations.
In this revision, we have addressed all comments and improved the
manuscript in a focused way without altering the core empirical evidence.
The main revisions include:
\begin{enumerate}
  \item stronger economic interpretation of the medium- and long-scale
    spillover results, including their implications for market integration;
  \item clearer positioning of the deep-learning comparison as a
    controlled benchmark rather than an exhaustive sequential-model sweep;
  \item more explicit discussion of the practical economic significance of
    the forecasting and warning gains; and
  \item improved signposting for finance-oriented readers in the
    methodology and discussion sections.
\end{enumerate}

The revised manuscript remains fully based on public data and a strict
walk-forward protocol. All preprocessing, wavelet decomposition,
calibration, and warning-threshold estimation are carried out within each
rolling training window to preserve causal integrity and avoid look-ahead
bias.

For transparency, we have also prepared point-by-point responses to both
reviewers and include them as non-published revision materials.

This manuscript is original work, has not been published elsewhere, and is
not under consideration by any other journal. All authors have read and
approved the revised version. There is no authorship change in this
revision.

Thank you for your time and consideration.

\closing{Sincerely,}

\ps{Funding: This research received no external funding. Conflicts of
interest: The authors declare no conflicts of interest.}

\end{letter}
\end{document}
